% Braden Simpson
% Lab 2, Astronomy 101
\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{fixltx2e}
% Correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% Begin the paper here
\begin{document}

% Paper title
\title{Positions of the Planets \\ Lab 2 \\ Astronomy 101}
% Authors names
\author{
Braden Simpson \\ braden@uvic.ca \\ V00685500
}
% make the title area
\maketitle

\section{Objective}
This lab’s purpose is to educate the student with the planets, how they move relative to each other, how their position plays a role in what planets can be seen, and what the configurations of planets are.  Finally the student will be able to make predictions about where planets will be in the sky.
\section{Introduction}
In this lab, there will be plotting of planets on coordinate and constellation maps, based on heliocentric values.  These plottings will then be used to give orbits and semi-accurately predict where the planets will be at times in the year.
\section{Equipment}
\begin{list}{*}{}
\item Large sheet of Polar coordinate graph paper
\item Protractor
\item SC001 Constellation chart
\item Coloured pencils
\item Planisphere
\end{list}
\section{Procedure}
\subsection{Plotting Planets}
The planets data was given in heliocentric coordinates, for given times of the year.  From those coordinates, the planets were plotted on the Polar coordinate graph paper, using coloured pencils to differentiate between the dates.  The data was given in the form of two tables, one which had the heliocentric longitudes of the planets, and another with the Astronomical Unit distance of the planets.  In order to do this plotting, the orbits were assumed to be circular. 
\subsection{Conjunctions, Elongations, and Oppositions}
In this section, the planets that have been plotted will have their configuration determined, and whether or not they are visible at sunrise, sunset, noon, and midnight.  This can all be determined based on their position relative to the earth and sun.
\subsection{Geocentric Ecliptic Longitude of the Planets}
In this section, instead of plotting the planets heliocentrically, they will be plotted using the geocentric ecliptic longitude, meaning that the results will be relative to the earth.  This will give the approximate constellation, right ascension, and declination of the planets, allowing the planets to be found from earth.  After getting the geocentric ecliptic longitude from the polar coordinate map, then they can be plotted on the SC001 Constellation chart.
\subsection{Use of a Planisphere}
A planisphere can plot the stars in the sky, based on time of day and date of the year.  The visible sky 
\section{Observations}
\subsection{Constellations}
See attached constellation diagrams.

\subsubsection{Andromeda}
Andromeda is located north of the celestial equator, and is only visible north of 40 degrees south latitude. \cite{andromedastarmap} It is a very large constellation an area of 722 square degrees.
\paragraph{Mythology:}
Andromeda was the beautiful daughter of Cassiopeia, who was chained to a rock in the sea by Poseidon, to be eaten by the sea monster Cetus.  This happened because Andromeda's father, Cepheus was the king of Aethiopia, and the only way to save his kingdom would be to sacrifice his daughter.  The daughter was saved by Perseus, who wielded the head of the medusa and turned the monster Cetus to stone.
\paragraph{Stars}
Andromeda is interesting because it's brightest star \emph{Alpheratz} with a magnitude of 2.1 and a distance of 97 light-years from Earth, is also the beginning of another constellation, \emph{Pegasus}.  There are also two more notable stars (there are more but I was only able to easily discern three when drawing it during the lab), \emph{Mirach}, and \emph{Almach}.

\subsubsection{Cepheus}
Located near Cassiopeia, and Polaris, Cepheus is shaped somewhat like a sideways child's drawing of a house.
\paragraph{Mythology}
Cepheus was the king of Aethiopia, father of Andromeda, and husband of Cassiopeia.  Cepheus offered his daughter as a sacrifice to save his kingdom, but was always praying for her to live. After Perseus came to save Andromeda from the sea monster Cetus, he allowed Perseus to marry Andromeda instead of his brother Phineus. \cite{cepheusmyth}
\subsubsection{Perseus}
\paragraph{Mythology}
Perseus is the hero who slain the gorgon Medusa and carries her head.  He used the Medusa head to turn the monster Cetus to stone. \cite{perseusmyth} 
\paragraph{Stars}
Perseus is home to \emph{Mirfak} ($\alpha$ Per), the brightest star, which is a supergiant, with luminosity 5,000 times and it's diameter 42 times that of our sun. \\ \cite{perseusstarmap}
Perseus also contains the star \emph{Algol} ($\beta$ Per), which is also known as "Demon Head", because it is the eye of the gorgon Medusa.  It is approximately 92.8 light-years from Earth.  One of the interesting parts of Algol is that is a variable magnitude star from a minimum of 3.5 to a maximum of 2.3, with a period of 2.867 days. \cite{perseus}
\subsubsection{Aquila}
Located in the northern sky, it lies a few degrees north of the celestial equator.  Altair, the constellation's brightest star is a vertex of the Summer Triangle asterism.
\paragraph{Mythology}
Aquila is believed to have been the bird that carried Zues' thunderbolts.  It is also said that Aquila is the eagle who kidnapped Ganymede. 
\paragraph{Stars}
The three main stars of Aquila are \emph{Altair}, \emph{Alshain}, and \emph{Tarazed}
\subsection{The Stars}
\subsubsection{Albireo}
Albireo is interesting because it is a double star, Albireo A, which is red and a magnitude of 3.1, and Albireo B, blue and magnitude 5.1.  Albireo A, burns cooler (approximately 4000K at its hottest whereas B burns at approximately 13000K) 
\subsection{Deep Sky Objects}
Sketches can be found attached in pen.
\subsubsection{Globular Cluster}
\paragraph{Messier 15 (M15)}
A globular cluster with approximately 100,000 stars, approximately 33,000 light-years away and 12 billion years old.  M15 has a supermassive black hole in the center, which holds the stars in, in a tight gravitational pull.
\subsubsection{Open Cluster}
\paragraph{Messier 11 (M11)}
Open cluster with approximately 3000 stars, which are all similar in age, since they were formed from one very large clump of gas approximately 1000 light years from Earth.  Open clusters are loosely bound by mutual gravitational pull, which is different from \emph{Globular Clusters}.
\subsubsection{Planetary Nebula}
A planetary nebula consists of expanding gas.  They are essential to the chemical evolution of the galaxy, meaning they are good for returning materials that have been enriched back to the galaxy.
\paragraph{M57 -- Ring Nebula}
M57 is a great example of a planetary nebula because it contains a now white dwarf , that had gone supernova and exploded, sending gas expanding back into the galaxy.  It is approximately 2300 light years away.\cite{ringnebula}    
\subsubsection{Galaxy}
A galaxy is a large grouping of stars, gas, dust, and other objects that are bound together by gravity.  There are estimated to be more than 170 billion galaxies in the observable universe, one of which is our Milky Way galaxy.
\paragraph{Andromeda -- M31}
Andromeda is another spiral galaxy nearest to our own, at an approximate distance of 2.5 million light years away.  The interesting thing about the Andromeda galaxy is that it is one of the brightest spiral galaxies, making it slightly visible to the naked eye on some nights.  
\section{Conclusion}
This lab was a success in that I know a lot more about many new constellations including the four included in the report as well as more such as Signus, and Saggitarius.  I also have knowledge about two types of telescope, reflective and refractive, and the uses of both, in addition to being able to operate one.  
\bibliographystyle{IEEEtran}
\bibliography{lab1}
\end{document}